\bf Properties and Bayes fitting of restricted Boltzmann machines

### 2017-07-09 writing/paper-rbm/chapters/rbm.Rmd
small edits

The concepts of weight-decay (penalization) and sparsity (regularization) are suggested in the literature as practical remedies for both over-fitting and poor mixing in the Markov chain during fitting [@hinton2010practical; @tieleman2008training; @cho2012tikhonov]. Both $L_1$ and $L_2$ type penalties are mentioned to achieve weight-decay however it is unclear the benefits of these particular forms in different situations. Additionally, it is not clear the degree to which regularization and penalization are used by practitioners because they are not (by default) a part of the accepted fitted methodology [@hinton2002training; @carreira2005contrastive]. In this paper, we attempt to address the concerns with overfitting and poor mixing via specification of a Bayesian prior in Section \@ref(bayesian-model-fitting).

>>>>

Notions of weight-decay (penalization) and sparsity (regularization) have been suggested in the RBM literature as practical remedies for both over-fitting and poor mixing in the Markov chain during fitting [@hinton2010practical; @tieleman2008training; @cho2012tikhonov]. Both $L_1$ and $L_2$ type penalties are mentioned to achieve weight-decay, though the benefits of these particular forms are unknown in different situations. However,  the degree to which regularization and penalization are used by practitioners is not clear because these concepts are not (by default) a part of the accepted fitted methodology [@hinton2002training; @carreira2005contrastive]. In this paper, we attempt to address the concerns with overfitting and poor mixing in an alternative, and perhaps more transparent manner, via specification of a Bayesian prior in Section \@ref(bayesian-model-fitting).

### 2017-07-09 writing/paper-rbm/docs/paper.tex
small edits

The concepts of weight-decay (penalization) and sparsity
(regularization) are suggested in the literature as practical remedies
for both over-fitting and poor mixing in the Markov chain during fitting
(Hinton \protect\hyperlink{ref-hinton2010practical}{2010}; Tieleman
\protect\hyperlink{ref-tieleman2008training}{2008}; Cho, Ilin, and Raiko
\protect\hyperlink{ref-cho2012tikhonov}{2012}). Both \(L_1\) and \(L_2\)
type penalties are mentioned to achieve weight-decay however it is
unclear the benefits of these particular forms in different situations.
Additionally, it is not clear the degree to which regularization and
penalization are used by practitioners because they are not (by default)
a part of the accepted fitted methodology (Hinton
\protect\hyperlink{ref-hinton2002training}{2002}; Carreira-Perpinan and
Hinton \protect\hyperlink{ref-carreira2005contrastive}{2005}). In this
paper, we attempt to address the concerns with overfitting and poor
mixing via specification of a Bayesian prior in Section
\ref{bayesian-model-fitting}.

>>>>

Notions of weight-decay (penalization) and sparsity (regularization)
have been suggested in the RBM literature as practical remedies for both
over-fitting and poor mixing in the Markov chain during fitting (Hinton
\protect\hyperlink{ref-hinton2010practical}{2010}; Tieleman
\protect\hyperlink{ref-tieleman2008training}{2008}; Cho, Ilin, and Raiko
\protect\hyperlink{ref-cho2012tikhonov}{2012}). Both \(L_1\) and \(L_2\)
type penalties are mentioned to achieve weight-decay, though the
benefits of these particular forms are unknown in different situations.
However, the degree to which regularization and penalization are used by
practitioners is not clear because these concepts are not (by default) a
part of the accepted fitted methodology (Hinton
\protect\hyperlink{ref-hinton2002training}{2002}; Carreira-Perpinan and
Hinton \protect\hyperlink{ref-carreira2005contrastive}{2005}). In this
paper, we attempt to address the concerns with overfitting and poor
mixing in an alternative, and perhaps more transparent manner, via
specification of a Bayesian prior in Section
\ref{bayesian-model-fitting}.
